### 2020-01-18 Temp_tables/table_3.tex
intend tables

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:55:48
\begin{table}[!htbp] \centering 
  \caption{Additional controls} 
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\ 
\cline{2-5} 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.275$^{*}$ & $-$0.320$^{**}$ & $-$0.331$^{**}$ & $-$0.378$^{**}$ \\ 
  & (0.166) & (0.145) & (0.155) & (0.160) \\ 
   SPZ_c \times \text{Period} \times \text{Polluted}_i  & 0.081 & 0.070 & 0.004 & 0.019 \\ 
  & (0.158) & (0.147) & (0.155) & (0.161) \\ 
   Coastal_c \times \text{Period} \times \text{Polluted}_i  & $-$0.083 & $-$0.034 & $-$0.034 & $-$0.044 \\ 
  & (0.148) & (0.150) & (0.153) & (0.161) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}  & 1.531 &  &  &  \\ 
  & (1.185) &  &  &  \\ 
   SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}  & 0.181 &  &  &  \\ 
  & (1.054) &  &  &  \\ 
   Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}  & 0.077 &  &  &  \\ 
  & (1.091) &  &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &  & 1.305$^{*}$ &  &  \\ 
  &  & (0.749) &  &  \\ 
   SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &  & 0.300 &  &  \\ 
  &  & (0.689) &  &  \\ 
   Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &  & $-$0.327 &  &  \\ 
  &  & (0.774) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  &  & 0.924 &  \\ 
  &  &  & (0.595) &  \\ 
   SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  &  & 0.477 &  \\ 
  &  &  & (0.544) &  \\ 
   Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  &  & $-$0.150 &  \\ 
  &  &  & (0.559) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  &  & 1.391$^{*}$ \\ 
  &  &  &  & (0.725) \\ 
   SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  &  & 0.525 \\ 
  &  &  &  & (0.666) \\ 
   Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  &  & $-$0.142 \\ 
  &  &  &  & (0.723) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.851 & 0.851 & 0.851 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{4}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{4}{l}{are clustered by city} \\ 
\end{tabular} 
\end{adjustbox}
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:55:48
\begin{table}[!htbp] \centering
  \caption{Additional controls}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \hline \\[-1.8ex]
      TCZ_c \times \text{Period} \times \text{Polluted}_i                                         & $-$0.275$^{*}$ & $-$0.320$^{**}$ & $-$0.331$^{**}$ & $-$0.378$^{**}$ \\
                                                                                                  & (0.166)        & (0.145)         & (0.155)         & (0.160)         \\
      SPZ_c \times \text{Period} \times \text{Polluted}_i                                         & 0.081          & 0.070           & 0.004           & 0.019           \\
                                                                                                  & (0.158)        & (0.147)         & (0.155)         & (0.161)         \\
      Coastal_c \times \text{Period} \times \text{Polluted}_i                                     & $-$0.083       & $-$0.034        & $-$0.034        & $-$0.044        \\
                                                                                                  & (0.148)        & (0.150)         & (0.153)         & (0.161)         \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}       & 1.531          &                 &                 &                 \\
                                                                                                  & (1.185)        &                 &                 &                 \\
      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}       & 0.181          &                 &                 &                 \\
                                                                                                  & (1.054)        &                 &                 &                 \\
      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}   & 0.077          &                 &                 &                 \\
                                                                                                  & (1.091)        &                 &                 &                 \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}      &                & 1.305$^{*}$     &                 &                 \\
                                                                                                  &                & (0.749)         &                 &                 \\
      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}      &                & 0.300           &                 &                 \\
                                                                                                  &                & (0.689)         &                 &                 \\
      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &                & $-$0.327        &                 &                 \\
                                                                                                  &                & (0.774)         &                 &                 \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}     &                &                 & 0.924           &                 \\
                                                                                                  &                &                 & (0.595)         &                 \\
      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}     &                &                 & 0.477           &                 \\
                                                                                                  &                &                 & (0.544)         &                 \\
      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i} &                &                 & $-$0.150        &                 \\
                                                                                                  &                &                 & (0.559)         &                 \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}      &                &                 &                 & 1.391$^{*}$     \\
                                                                                                  &                &                 &                 & (0.725)         \\
      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}      &                &                 &                 & 0.525           \\
                                                                                                  &                &                 &                 & (0.666)         \\
      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &                &                 &                 & $-$0.142        \\
                                                                                                  &                &                 &                 & (0.723)         \\
      \hline \\[-1.8ex]
      City-year fixed effects                                                                     & Yes            & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                                                                 & Yes            & Yes             & Yes             & Yes             \\
      City-industry fixed effects                                                                 & Yes            & Yes             & Yes             & Yes             \\
      Observations                                                                                & 30,676         & 30,676          & 30,676          & 30,676          \\
      R$^{2}$                                                                                     & 0.851          & 0.851           & 0.851           & 0.852           \\
      \hline
      \hline \\[-1.8ex]
      \textit{Note:}  & \multicolumn{4}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
      & \multicolumn{4}{l}{Heteroskedasticity-robust standard errors in parentheses} \\
      & \multicolumn{4}{l}{are clustered by city} \\
    \end{tabular}
  \end{adjustbox}
\end{table}

### 2020-01-18 Temp_tables/table_4.tex
intend tables

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:55:57
\begin{table}[!htbp] \centering 
  \caption{Additional controls (2)} 
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\ 
\cline{2-5} 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
   \text{Polluted}_i \times \text{ln gdp per cap)}_{ct}  & $-$0.038 & $-$0.034 & $-$0.029 & $-$0.036 \\ 
  & (0.297) & (0.298) & (0.298) & (0.297) \\ 
   \text{Polluted}_i \times \text{ln population)}_{ct}  & 0.165 & 0.170 & 0.172 & 0.172 \\ 
  & (0.227) & (0.228) & (0.228) & (0.228) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.238 & $-$0.280$^{**}$ & $-$0.317$^{**}$ & $-$0.360$^{**}$ \\ 
  & (0.153) & (0.142) & (0.151) & (0.156) \\ 
   TCZ_c \times \text{Period} \times \text{count share SOE}_{i}  & $-$1.177 &  &  &  \\ 
  & (0.888) &  &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}  & 1.522 &  &  &  \\ 
  & (1.115) &  &  &  \\ 
   TCZ_c \times \text{Period} \times \text{output share SOE}_{i}  &  & $-$0.842 &  &  \\ 
  &  & (0.574) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &  & 1.327$^{*}$ &  &  \\ 
  &  & (0.731) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share SOE}_{i}  &  &  & $-$0.707 &  \\ 
  &  &  & (0.438) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  &  & 1.074$^{*}$ &  \\ 
  &  &  & (0.577) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share SOE}_{i}  &  &  &  & $-$1.044$^{*}$ \\ 
  &  &  &  & (0.562) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  &  & 1.545$^{**}$ \\ 
  &  &  &  & (0.709) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes \\ 
Observations & 30,195 & 30,195 & 30,195 & 30,195 \\ 
R$^{2}$ & 0.852 & 0.852 & 0.852 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{4}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{4}{l}{are clustered by city} \\ 
\end{tabular} 
\end{adjustbox}
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:55:57
\begin{table}[!htbp] \centering
  \caption{Additional controls (2)}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \hline \\[-1.8ex]
      \text{Polluted}_i \times \text{ln gdp per cap)}_{ct}                                    & $-$0.038 & $-$0.034        & $-$0.029        & $-$0.036        \\
                                                                                              & (0.297)  & (0.298)         & (0.298)         & (0.297)         \\
      \text{Polluted}_i \times \text{ln population)}_{ct}                                     & 0.165    & 0.170           & 0.172           & 0.172           \\
                                                                                              & (0.227)  & (0.228)         & (0.228)         & (0.228)         \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i                                     & $-$0.238 & $-$0.280$^{**}$ & $-$0.317$^{**}$ & $-$0.360$^{**}$ \\
                                                                                              & (0.153)  & (0.142)         & (0.151)         & (0.156)         \\
      TCZ_c \times \text{Period} \times \text{count share SOE}_{i}                            & $-$1.177 &                 &                 &                 \\
                                                                                              & (0.888)  &                 &                 &                 \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}   & 1.522    &                 &                 &                 \\
                                                                                              & (1.115)  &                 &                 &                 \\
      TCZ_c \times \text{Period} \times \text{output share SOE}_{i}                           &          & $-$0.842        &                 &                 \\
                                                                                              &          & (0.574)         &                 &                 \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &          & 1.327$^{*}$     &                 &                 \\
                                                                                              &          & (0.731)         &                 &                 \\
      TCZ_c \times \text{Period} \times \text{capital share SOE}_{i}                          &          &                 & $-$0.707        &                 \\
                                                                                              &          &                 & (0.438)         &                 \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i} &          &                 & 1.074$^{*}$     &                 \\
                                                                                              &          &                 & (0.577)         &                 \\
      TCZ_c \times \text{Period} \times \text{labour share SOE}_{i}                           &          &                 &                 & $-$1.044$^{*}$  \\
                                                                                              &          &                 &                 & (0.562)         \\
      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &          &                 &                 & 1.545$^{**}$    \\
                                                                                              &          &                 &                 & (0.709)         \\
      \hline \\[-1.8ex]
      City-year fixed effects                                                                 & Yes      & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                                                             & Yes      & Yes             & Yes             & Yes             \\
      City-industry fixed effects                                                             & Yes      & Yes             & Yes             & Yes             \\
      Observations                                                                            & 30,195   & 30,195          & 30,195          & 30,195          \\
      R$^{2}$                                                                                 & 0.852    & 0.852           & 0.852           & 0.852           \\
      \hline
      \hline \\[-1.8ex]
      \textit{Note:}  & \multicolumn{4}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
      & \multicolumn{4}{l}{Heteroskedasticity-robust standard errors in parentheses} \\
      & \multicolumn{4}{l}{are clustered by city} \\
    \end{tabular}
  \end{adjustbox}
\end{table}

### 2020-01-18 Temp_tables/table_6.tex
intend tables

\begin{table}[htbp]\centering
    \resizebox{1\textwidth}{!}{
        \begin{threeparttable}  
            \caption{\small Summary Statistics by City-industry characteristics and City characteristics}
            \begin{tabular}{lrrrr}
                \multicolumn{1}{l}{\textbf{Panel A: SOE dominated sector}} \\
                    \toprule
                    & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\ 
                    \cline{2-5} 
                    \\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
                    \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
                    \hline \\[-1.8ex] 
                    TCZ_c \times \text{Polluted}_i \times \text{Period}  & $-$0.123 & 0.101 & 0.114 & 0.235 \\ 
                    & (0.216) & (0.234) & (0.229) & (0.232) \\ 
                    \hline \\[-1.8ex] 
                    City-year fixed effects & Yes & Yes & Yes & Yes \\ 
                    Industry-year fixed effects & Yes & Yes & Yes & Yes \\
                    City-industry fixed effects & Yes & Yes & Yes & Yes \\
                    Observations & 9,232 & 9,824 & 10,423 & 10,076 \\ 
                    Number sectors & X & 92 & 104& 98 \\
                    R$^{2}$ & 0.888 & 0.865 & 0.869 & 0.862 \\
                    \bottomrule
                    \\ %%% Create second table
                \multicolumn{1}{l}{\textbf{Panel B: SOE dominating sector}} \\
                    \toprule
                    & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\ 
                    \cline{2-5} 
                    \\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
                    \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
                    \hline \\[-1.8ex] 
                    TCZ_c \times \text{Polluted}_i \times \text{Period}  & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\ 
                    & (0.145) & (0.124) & (0.124) & (0.125) \\ 
                    \hline \\[-1.8ex] 
                    City-year fixed effects & Yes & Yes & Yes & Yes \\ 
                    Industry-year fixed effects & Yes & Yes & Yes & Yes \\
                    City-industry fixed effects & Yes & Yes & Yes & Yes \\
                    Observations & 21,444 & 20,852 & 20,253 & 20,600 \\ 
                    Number sectors & X & 204 & 192& 198 \\
                    R$^{2}$ & 0.849 & 0.857 & 0.853 & 0.858 \\ 
            \end{tabular}
            \begin{tablenotes}
                \small
                \item Panel A 
                Panel B \\
                Sources: Author's own computation 
            \end{tablenotes}
        \end{threeparttable}
    }
\end{table}

>>>>

\begin{table}[htbp]\centering
  \resizebox{1\textwidth}{!}{
    \begin{threeparttable}
      \caption{\small Summary Statistics by City-industry characteristics and City characteristics}
      \begin{tabular}{lrrrr}
        \multicolumn{1}{l}{\textbf{Panel A: SOE dominated sector}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_c \times \text{Polluted}_i \times \text{Period} & $-$0.123 & 0.101           & 0.114           & 0.235           \\
                                                            & (0.216)  & (0.234)         & (0.229)         & (0.232)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 9,232    & 9,824           & 10,423          & 10,076          \\
        Number sectors                                      & X        & 92              & 104             & 98              \\
        R$^{2}$                                             & 0.888    & 0.865           & 0.869           & 0.862           \\
        \bottomrule
        \\ %%% Create second table
        \multicolumn{1}{l}{\textbf{Panel B: SOE dominating sector}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_c \times \text{Polluted}_i \times \text{Period} & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                            & (0.145)  & (0.124)         & (0.124)         & (0.125)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 21,444   & 20,852          & 20,253          & 20,600          \\
        Number sectors                                      & X        & 204             & 192             & 198             \\
        R$^{2}$                                             & 0.849    & 0.857           & 0.853           & 0.858           \\
      \end{tabular}
      \begin{tablenotes}
        \small
        \item Panel A
        Panel B \\
        Sources: Author's own computation
      \end{tablenotes}
    \end{threeparttable}
  }
\end{table}
